### 2022-04-26 tables/bacon_decomposition_Assault.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionAssault}Bacon Decomposition: Assault Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.1487745} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{0.0079628}\\
Later vs Always Treated & -0.0314314 & 0.1589397 & 0.0009728\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{-0.0174274} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{-0.0034427}\\
Treated vs Untreated & -0.2207888 & 0.7492871 & -0.1375213\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.1320284}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionAssault}Bacon Decomposition - Assault Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.149} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{0.008}\\
Later vs Always Treated & -0.031 & 0.159 & 0.001\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{-0.017} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-0.003}\\
Treated vs Untreated & -0.221 & 0.749 & -0.138\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.132}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Autotheft.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionAutotheft}Bacon Decomposition: Autotheft Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.0887179} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{0.0056843}\\
Later vs Always Treated & 0.1885142 & 0.1589397 & 0.0336117\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.0994063} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{0.0020305}\\
Treated vs Untreated & 0.0086094 & 0.7492871 & 0.0262756\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.0676020}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionAutotheft}Bacon Decomposition - Autotheft Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.089} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{0.006}\\
Later vs Always Treated & 0.189 & 0.159 & 0.034\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.099} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{0.002}\\
Treated vs Untreated & 0.009 & 0.749 & 0.026\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.068}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Burglary.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionBurglary}Bacon Decomposition: Burglary Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{-0.0146061} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{-0.0023226}\\
Later vs Always Treated & 0.0169005 & 0.1589397 & 0.0048413\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{-0.0157802} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{-0.0013013}\\
Treated vs Untreated & -0.0068820 & 0.7492871 & 0.0064291\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.0076465}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionBurglary}Bacon Decomposition - Burglary Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{-0.015} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{-0.002}\\
Later vs Always Treated & 0.017 & 0.159 & 0.005\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{-0.016} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-0.001}\\
Treated vs Untreated & -0.007 & 0.749 & 0.006\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.008}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Larceny.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionLarceny}Bacon Decomposition: Larceny Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.0088734} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{-0.0004160}\\
Later vs Always Treated & 0.0477985 & 0.1589397 & 0.0080003\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.0616798} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{0.0004859}\\
Treated vs Untreated & 0.0346292 & 0.7492871 & 0.0280699\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.0361400}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionLarceny}Bacon Decomposition - Larceny Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{0.000}\\
Later vs Always Treated & 0.048 & 0.159 & 0.008\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.062} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{0.000}\\
Treated vs Untreated & 0.035 & 0.749 & 0.028\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.036}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Murder.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionMurder}Bacon Decomposition: Murder Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.0545024} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{0.0054525}\\
Later vs Always Treated & -0.0384771 & 0.1589397 & -0.0012542\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.0188246} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{0.0000418}\\
Treated vs Untreated & -0.0848318 & 0.7492871 & -0.0415959\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.0373558}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionMurder}Bacon Decomposition - Murder Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.055} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{0.005}\\
Later vs Always Treated & -0.038 & 0.159 & -0.001\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.019} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{0.000}\\
Treated vs Untreated & -0.085 & 0.749 & -0.042\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.037}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Property.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionProperty}Bacon Decomposition: Property Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.0036098} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{-0.0007191}\\
Later vs Always Treated & 0.0504242 & 0.1589397 & 0.0085564\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.0490119} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{0.0001507}\\
Treated vs Untreated & 0.0238073 & 0.7492871 & 0.0210569\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.0290449}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionProperty}Bacon Decomposition - Property Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.004} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{-0.001}\\
Later vs Always Treated & 0.050 & 0.159 & 0.009\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.049} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{0.000}\\
Treated vs Untreated & 0.024 & 0.749 & 0.021\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.029}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Rape.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionRape}Bacon Decomposition: Rape Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{-0.0264193} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{-0.0026425}\\
Later vs Always Treated & -0.2001560 & 0.1589397 & -0.0305273\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{-0.0106483} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{-0.0019283}\\
Treated vs Untreated & -0.0030557 & 0.7492871 & 0.0030423\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.0320558}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionRape}Bacon Decomposition - Rape Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{-0.026} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{-0.003}\\
Later vs Always Treated & -0.200 & 0.159 & -0.031\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{-0.011} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-0.002}\\
Treated vs Untreated & -0.003 & 0.749 & 0.003\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.032}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Robbery.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionRobbery}Bacon Decomposition: Robbery Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.0961047} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{0.0073682}\\
Later vs Always Treated & 0.0940074 & 0.1589397 & 0.0174822\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.1505417} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{0.0020947}\\
Treated vs Untreated & -0.0263060 & 0.7492871 & -0.0100514\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.0168936}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionRobbery}Bacon Decomposition - Robbery Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.096} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{0.007}\\
Later vs Always Treated & 0.094 & 0.159 & 0.017\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.151} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{0.002}\\
Treated vs Untreated & -0.026 & 0.749 & -0.010\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{0.017}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/bacon_decomposition_Violent.tex
updates to cs, draft section
final push

\caption{\label{tab:tab:bacondecompositionViolent}Bacon Decomposition: Violent Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.1000224} & \cellcolor{gray!6}{0.0683810} & \cellcolor{gray!6}{0.0051705}\\
Later vs Always Treated & -0.0596393 & 0.1589397 & -0.0044690\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.0208665} & \cellcolor{gray!6}{0.0233921} & \cellcolor{gray!6}{-0.0017883}\\
Treated vs Untreated & -0.1422163 & 0.7492871 & -0.0839315\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.0850183}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:bacondecompositionViolent}Bacon Decomposition - Violent Crime Rate Log}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Type & Average Estimate & Group Weight & Weighted Estimate\\
\midrule
\cellcolor{gray!6}{Earlier vs Later Treated} & \cellcolor{gray!6}{0.100} & \cellcolor{gray!6}{0.068} & \cellcolor{gray!6}{0.005}\\
Later vs Always Treated & -0.060 & 0.159 & -0.004\\
\cellcolor{gray!6}{Later vs Earlier Treated} & \cellcolor{gray!6}{0.021} & \cellcolor{gray!6}{0.023} & \cellcolor{gray!6}{-0.002}\\
Treated vs Untreated & -0.142 & 0.749 & -0.084\\
\cellcolor{gray!6}{Total TWFE} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{NaN} & \cellcolor{gray!6}{-0.085}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/cs.tex
final push

\caption{\label{tab:tab:cs}Callaway and Sant'anna Overall ATTs}
\centering
\begin{tabular}[t]{lrr}
\toprule
Outcome Variable & Overall ATT & Std. Error\\
\midrule
\cellcolor{gray!6}{Violent Crime Rate Log} & \cellcolor{gray!6}{-0.0099595} & \cellcolor{gray!6}{0.0259180}\\
Property Crime Rate Log & 0.0129076 & 0.0128726\\
\cellcolor{gray!6}{Murder Crime Rate Log} & \cellcolor{gray!6}{-0.0485681} & \cellcolor{gray!6}{0.0266759}\\
Rape Crime Rate Log & 0.0200170 & 0.0284581\\
\cellcolor{gray!6}{Assault Crime Rate Log} & \cellcolor{gray!6}{0.0048334} & \cellcolor{gray!6}{0.0444671}\\
\addlinespace
Robbery Crime Rate Log & 0.0387509 & 0.0344164\\
\cellcolor{gray!6}{Burglary Crime Rate Log} & \cellcolor{gray!6}{-0.0157512} & \cellcolor{gray!6}{0.0161027}\\
Larceny Crime Rate Log & 0.0302561 & 0.0165051\\
\cellcolor{gray!6}{Autotheft Crime Rate Log} & \cellcolor{gray!6}{0.0107402} & \cellcolor{gray!6}{0.0427668}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:cs}Callaway and Sant'anna Overall ATTs}
\centering
\begin{tabular}[t]{lrr}
\toprule
Outcome Variable & Overall ATT & Std. Error\\
\midrule
\cellcolor{gray!6}{Violent Crime Rate Log} & \cellcolor{gray!6}{-0.010} & \cellcolor{gray!6}{0.025}\\
Property Crime Rate Log & 0.013 & 0.012\\
\cellcolor{gray!6}{Murder Crime Rate Log} & \cellcolor{gray!6}{-0.049} & \cellcolor{gray!6}{0.027}\\
Rape Crime Rate Log & 0.020 & 0.028\\
\cellcolor{gray!6}{Assault Crime Rate Log} & \cellcolor{gray!6}{0.005} & \cellcolor{gray!6}{0.041}\\
\addlinespace
Robbery Crime Rate Log & 0.039 & 0.033\\
\cellcolor{gray!6}{Burglary Crime Rate Log} & \cellcolor{gray!6}{-0.016} & \cellcolor{gray!6}{0.016}\\
Larceny Crime Rate Log & 0.030 & 0.016\\
\cellcolor{gray!6}{Autotheft Crime Rate Log} & \cellcolor{gray!6}{0.011} & \cellcolor{gray!6}{0.041}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/rep_table_2a.tex
final push

\caption{\label{tab:tab:replicatetable2a}Main Variables Summary}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Variable & N & Mean & Standard Deviation\\
\midrule
\cellcolor{gray!6}{Shalll} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.1912} & \cellcolor{gray!6}{0.3935}\\
Violent Arrest Rate & 802 & 41.0906 & 22.2036\\
\cellcolor{gray!6}{Property Arrest Rate} & \cellcolor{gray!6}{809} & \cellcolor{gray!6}{16.9180} & \cellcolor{gray!6}{4.6770}\\
Murder Arrest Rate & 806 & 91.2989 & 55.9428\\
\cellcolor{gray!6}{Rape Arrest Rate} & \cellcolor{gray!6}{799} & \cellcolor{gray!6}{41.0231} & \cellcolor{gray!6}{17.3887}\\
\addlinespace
Assault Arrest Rate & 809 & 44.6250 & 16.9783\\
\cellcolor{gray!6}{Robery Arrest Rate} & \cellcolor{gray!6}{808} & \cellcolor{gray!6}{31.4581} & \cellcolor{gray!6}{13.5928}\\
Burglary Arrest Rate & 809 & 13.8044 & 4.5712\\
\cellcolor{gray!6}{Larceny Arrest Rate} & \cellcolor{gray!6}{809} & \cellcolor{gray!6}{18.5372} & \cellcolor{gray!6}{5.1961}\\
Autotheft Arrest Rate & 808 & 22.3455 & 37.6114\\
\addlinespace
\cellcolor{gray!6}{Violent Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{483.9260} & \cellcolor{gray!6}{318.9425}\\
Property Crime Rate & 816 & 4618.3394 & 1210.4646\\
\cellcolor{gray!6}{Murder Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{7.7683} & \cellcolor{gray!6}{6.8817}\\
Rape Crime Rate & 816 & 33.9818 & 15.0721\\
\cellcolor{gray!6}{Assault Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{278.7551} & \cellcolor{gray!6}{159.6495}\\
\addlinespace
Robbery Crime Rate & 816 & 163.4208 & 176.2506\\
\cellcolor{gray!6}{Burglary Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{1239.3364} & \cellcolor{gray!6}{417.7576}\\
Larceny Crime Rate & 816 & 2968.7079 & 751.0234\\
\cellcolor{gray!6}{Autotheft Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{410.2951} & \cellcolor{gray!6}{231.1537}\\
Personal Income Rpc & 816 & 9351.8205 & 4689.7012\\
\addlinespace
\cellcolor{gray!6}{Unemployment Insurance Rpc} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{50.0187} & \cellcolor{gray!6}{38.0808}\\
Income Maintenance Rpc & 816 & 115.2756 & 70.9528\\
\cellcolor{gray!6}{Retirement Payments Rpc} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{1002.2257} & \cellcolor{gray!6}{546.4679}\\
State Population & 816 & 4646787.3419 & 5010349.8734\\
\cellcolor{gray!6}{Density} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{355.9729} & \cellcolor{gray!6}{1408.2501}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:replicatetable2a}Main Variables Summary}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Variable & N & Mean & Standard Deviation\\
\midrule
\cellcolor{gray!6}{Shalll} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.191} & \cellcolor{gray!6}{0.393}\\
Violent Arrest Rate & 802 & 41.091 & 22.204\\
\cellcolor{gray!6}{Property Arrest Rate} & \cellcolor{gray!6}{809} & \cellcolor{gray!6}{16.918} & \cellcolor{gray!6}{4.677}\\
Murder Arrest Rate & 806 & 91.299 & 55.943\\
\cellcolor{gray!6}{Rape Arrest Rate} & \cellcolor{gray!6}{799} & \cellcolor{gray!6}{41.023} & \cellcolor{gray!6}{17.389}\\
\addlinespace
Assault Arrest Rate & 809 & 44.625 & 16.978\\
\cellcolor{gray!6}{Robery Arrest Rate} & \cellcolor{gray!6}{808} & \cellcolor{gray!6}{31.458} & \cellcolor{gray!6}{13.593}\\
Burglary Arrest Rate & 809 & 13.804 & 4.571\\
\cellcolor{gray!6}{Larceny Arrest Rate} & \cellcolor{gray!6}{809} & \cellcolor{gray!6}{18.537} & \cellcolor{gray!6}{5.196}\\
Autotheft Arrest Rate & 808 & 22.345 & 37.611\\
\addlinespace
\cellcolor{gray!6}{Violent Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{483.926} & \cellcolor{gray!6}{318.943}\\
Property Crime Rate & 816 & 4618.339 & 1210.465\\
\cellcolor{gray!6}{Murder Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{7.768} & \cellcolor{gray!6}{6.882}\\
Rape Crime Rate & 816 & 33.982 & 15.072\\
\cellcolor{gray!6}{Assault Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{278.755} & \cellcolor{gray!6}{159.650}\\
\addlinespace
Robbery Crime Rate & 816 & 163.421 & 176.251\\
\cellcolor{gray!6}{Burglary Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{1239.336} & \cellcolor{gray!6}{417.758}\\
Larceny Crime Rate & 816 & 2968.708 & 751.023\\
\cellcolor{gray!6}{Autotheft Crime Rate} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{410.295} & \cellcolor{gray!6}{231.154}\\
Personal Income Rpc & 816 & 9351.821 & 4689.701\\
\addlinespace
\cellcolor{gray!6}{Unemployment Insurance Rpc} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{50.019} & \cellcolor{gray!6}{38.081}\\
Income Maintenance Rpc & 816 & 115.276 & 70.953\\
\cellcolor{gray!6}{Retirement Payments Rpc} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{1002.226} & \cellcolor{gray!6}{546.468}\\
State Population & 816 & 4646787.342 & 5010349.873\\
\cellcolor{gray!6}{Density} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{355.973} & \cellcolor{gray!6}{1408.250}\\
\bottomrule
\end{tabular}
\end{table}
